Tropical mathematics and the Lambda-calculus I

### 2023-08-02 CSL24/section4.tex
commit

%Before looking at what happens in the case of non-linear programs, let us make the metric structure of $\LREL$ explicit. 
Observe that on the hom-sets $\HOM{\LREL_{!}}{X}{Y}$ there are two natural notions of distance: the metric $\| f-g\|_{\infty}$ arising from the norm and the one arising from the usual $\sup$-metric $d_\infty(f,g):=\sup_{a\in X} d_\infty(f^{!}(x),f^{!}(y))$.
In general one has $\| f-g\|_{\infty}\geq d_\infty(f,g)$, the equality holding when $f,g$ are linear.

>>>>

%Before looking at what happens in the case of non-linear programs, let us make the metric structure of $\LREL$ explicit. 
Observe that on the hom-sets $\HOM{\LREL_{!}}{X}{Y}$ there are two natural notions of distance: the metric $\| f-g\|_{\infty}$ arising from the norm and the one arising from the usual $\sup$-metric $d_\infty(f,g):=\sup_{a\in X} d_\infty(f^{!}(a),g^{!}(a))$.
In general one has $\| f-g\|_{\infty}\geq d_\infty(f,g)$, the equality holding when $f^{!},g^{!}$ are linear (i.e.~when they arise from morphisms of $ \LREL(X,Y)$).
